Exploring how changes in cause of death have narrowed the black-white life

### 2017-06-02 conferences/Max_planck_submission.Rmd

>>>>

**Note:** This file is based on **OLD** results that no longer exist. I have not updated this file to work with the new results since I have yet to re-run this code and check that all lines are correct. Thus, this file is kept for historical purposes and in case I would like to refer back to it to recreate some of the analysis/vis using the same results.

This file contains the code/analysis for my submission to the Max Planck Institute of Demography's symposium on the Human Mortality Database. The symposium was held in Berlin on May 22 and 23. My final presentation slides for the symposium can be found in the same folder as this submission and are based on updated results.
